---
title: "HW 1"
author: "BR Hoover"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(estimatr)
library(car)
library(magrittr)
library(texreg)

df<-read.csv("HPRICE2.csv")
```

```{r q1, echo=FALSE}
# estimate models
price_lm <- lm(data = df, formula = price ~ nox + rooms + stratio)

# summary with cluster-robust SEs
#summary(price_lm, cluster="cluster_id") 

# create table in stargazer
#stargazer(price_lm)

price_rlm<-lm_robust(data = df, formula = price ~ nox + rooms + stratio)

int<-price_rlm$coef[1]
nox<-price_rlm$coef[2]
room<-price_rlm$coef[3]
str<-price_rlm$coef[4]

table<-texreg(price_lm, include.ci = FALSE)
```

`r table`


(a) What is the effect of adding an additional room on the house price, holding NOx concentrations and student-teacher ratio constant?  


 
An extraroom will increase the price of the house by $`r room`

(b) What is the estimated effect on house values of reducing NOx concentrations by 2.5 parts per 100 million?  

(c) What percent of the variation in house values is explained by NOx concentrations, number of rooms, and student-teacher ratio?  

(d) What is the predicted value of a house with NOx concentrations of 6, with 7 rooms, and a student-teacher ratio of 20? The actual price for that house was $20,000. Did the buyer overpay for this house?  

(e) Test the null hypothesis that $β_{1}$ equals zero.  

(f) Test the null hypothesis that $β_{1}$ and $β_{3}$ jointly equal zero.  

(g) Test the null hypothesis that $β_{1}$ = $β_{3}$.  

