---
title: "HW1"
author: "BR"
date: "24/01/2020"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(tidyverse)
library(estimatr)
library(car)

df<-read.csv("HPRICE2.csv")
```


```{r, include=FALSE}
price_rlm<-lm_robust(data = df, formula = price ~ nox + rooms + stratio)
summary(price_rlm)

int<-price_rlm$coef[1]
nox<-price_rlm$coef[2]
room<-price_rlm$coef[3]
str<-price_rlm$coef[4]
r_sq<-price_rlm$adj.r.squared
```

```{r, include=FALSE}
b_nox<-(-2.5)*nox #b

nox/(int+nox) #c
room/(int+room)
str/(int+str)

#57.08% (Adjusted R-squared score)

#NOx: 12.42192%  
#Room: 31.66241%
#Student Ratio: 9.991189%  

-(nox/(int+nox))+(room/(int+room))+-(str/(int+str))#not correct c?

#d

d_price<-round(int+nox*6+room*7+str*20, digits = 0)

```
a) What is the effect of adding an additional room on the house price, holding NOxconcentrations and student-teacher ratio constant?  

  An extra room will increase the house price by $`r round(room, digits = 2)`
<br><br>
b) What is the estimated effect on house values of reducing NOx concentrations by 2.5 partsper 100 million?  

  Reducing the NOx concentrations by 2.5 parts per 100 million will increase the value of the house by $`r round(b_nox, digits = 2)`  

<br><br>

c) What percent of the variation in house values is explained by NOx concentrations, number ofrooms, and student-teacher ratio?  
  
  `r round((100*r_sq), digits = 2)` %

<br><br>

d) What is the predicted value of a house with NOx concentrations of 6, with 7 rooms, and astudent-teacher ratio of 20? The actual price for that house was $20,000. Did the buyer overpayfor this house?  
    
  The predicted value of the house is $`r `. The buyer got a great deal on the house!

```{r, include = FALSE}
#e
linearHypothesis(price_rlm,c("nox=0"), white.adjust = "hc2")

e_c<-round(e$Chisq[2], digits = 2)
e_p<-e$`Pr(>Chisq)`
```

<br><br>
e) Test the null hypothesis that  

  Test-statistic is `r e_c`. We can reject the null hypothesis at the 5% interval that the coefficient is not zero. 
     
```{r, include=FALSE}
# TEST THAT NOX=0 & ROOMS=0
f<-linearHypothesis(price_rlm,c("nox=0", "rooms=0"), white.adjust = "hc2")
f_c<-round(f$Chisq[2], digits = 2)
f_p<-f$`Pr(>Chisq)`
```
 <br><br> 
f) Test the null hypothesis that jointly equal zero.  

  F-statistic for this joint hypothesis test is about `r f_c` and the corresponding p-value is <0.001 . Thus, we can reject the null hypothesis that both coefficients are zero




```{r, include=FALSE}
# TEST THAT 4*NOX=-ROOMS
g<-linearHypothesis(price_rlm,c("nox=stratio"), white.adjust = "hc2")
g_c<-round(g$Chisq[2], digits = 2)
g_p<-g$`Pr(>Chisq)`
```

<br><br>
g) Test the null hypothesis that  

  F-statistic for this joint hypothesis test is about `r g_c` and the corresponding p-value is `r g_p`. Thus, we cannot reject the null hypothesis that both coefficients are equal. 




