---
title: "HW1"
author: "BR"
date: "24/01/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(estimatr)
library(car)

df<-read.csv("HPRICE2.csv")
```

```{r}
df %>%
  gather(-price, key = "var", value = "value") %>% 
  ggplot(aes(x = value, y = price)) +
    geom_point() +
    facet_wrap(~ var, scales = "free") +
    theme_bw()
```

```{r}
price_lm<-lm(data = df, formula = price ~ nox + rooms + stratio)
summary(price_lm)

 
plot(price_lm)
```
```{r}
price_rlm<-lm_robust(data = df, formula = price ~ nox + rooms + stratio)
summary(price_rlm)

int<-price_rlm$coef[1]
nox<-price_rlm$coef[2]
room<-price_rlm$coef[3]
str<-price_rlm$coef[4]
```

```{r}
(-2.5)*nox #b

nox/(int+nox) #c
room/(int+room)
str/(int+str)

int+nox*6+room*7+str*20#d

# TEST THAT NOX=0, e
linearHypothesis(price_rlm,c("nox=0"), white.adjust = "hc2")

# TEST THAT NOX=0 & ROOMS=0
linearHypothesis(price_rlm,c("nox=0", "rooms=0"), white.adjust = "hc2")

# TEST THAT 4*NOX=-ROOMS
linearHypothesis(price_rlm,c("nox=stratio"), white.adjust = "hc2")
```

a) An extra room will increase the house price by $6,419

b) Increase house price by $3,827.061 

c) 
NOx: 12.42192%  
Room: 31.66241%
Student Ratio: 9.991189%  

d) $24,433.29
The buyer got a good deal. 

e) Rejecy Null. test-statistic is -6.915. We can reject the null hypothesis at the 5% interval that the coefficient is not zero. 

f) Reject null. They are no jointly 0.

F-statistic for this joint hypothesis test is about 295.09 and the corresponding p-value is < 2.2e-16. Thus, we can reject the null hypothesis that both coefficients are zero

g) Can't reject the null hypothesis. 

F-statistic for this joint hypothesis test is about 1.5561 and the corresponding p-value is 0.2122. Thus, we cannot reject the null hypothesis that both coefficients are equal. 
